\documentclass[letterpaper,11pt]{article}

\setcounter{secnumdepth}{0}
\usepackage{lipsum}
\usepackage{fancyhdr}
\usepackage[left=2.54cm, right=2.54cm, top=2.54cm, bottom=2.54cm]{geometry}

\thispagestyle{fancy}
\lhead{Phone: (516) 736-4987}
\chead{New York, NY}
\rhead{Email: kunal.bajpai@gmail.com}

\begin{document}

\section{Introduction}
\textbf{Masters in Computer Science} with \textbf{13+ years of experience} in Software Development

\section{Summary}
\begin{itemize}
    \item Currently working as \textbf{Lead Software Engineer} at \textbf{Broadridge}
    \item Strong \textbf{communication} \& \textbf{interpersonal} skills
    \item Strong \textbf{analytical} \& \textbf{problem-solving} skills
    \item In-depth experience working in \textbf{C\#}
    \item Advanced understanding of \textbf{agile methodologies} such as \textbf{CI/CD}, Application Resiliency, \& Security
    \item Proficient in all aspects of the Software Development Life Cycle
    \item Proficiency in automation \& continuous delivery methods
    \item Experience multiple programming language(s) \textbf{C\#}, \textbf{Python}, JavaScript, \textbf{BASH} Scripting
    \item Ambition to solve \textbf{tough} \& \textbf{challenging} problems using analytical methods
    \item Experience working with \textbf{distributed systems}
    \item Proficiency in creating \textbf{multi-threaded application} design \& development
    \item Competence in designing high-volume \textbf{ETL} jobs using \textbf{C\#}, Dotnet Core, \textbf{SSIS}
    \item Migration of legacy/monolith applications to \textbf{Microservice} using \textbf{Dotnet Core}
    \item Extensive Software Development on Distributed Platforms - Web Based \& Client Server Apps
    \item Competency in architecturing solutions using different \textbf{design patterns} namely \textbf{Singleton}, \textbf{Factory}, \textbf{Facade}, \textbf{Dependency Injection}, etc.
    \item Extensive exposure with \textbf{onsite/off-shore coordination}
    \item Result oriented \& self-motivated individual with full commitment towards creating value
    \item Quick learner, self-starter, individual contributor, \& \textbf{effective team player}
    \item Possess excellent interpersonal skills to interact with the \textbf{client/team members}
    \item Experience in dealing with \textbf{end users}, \textbf{gathering requirements}, \& coordinating all facets of a complex project
    \item Active participant in \textbf{interviewing} \& \textbf{hiring} new associates
\end{itemize}
\pagebreak

\section{Primary Skills}
\textbf{Dotnet Core} 7.0/6.0/5.0/3.1, \textbf{C\#}, \textbf{SSIS}, \textbf{Python}, \textbf{BASH}, Cygwin, \textbf{Linux}, Angular, HTML5, \textbf{TypeScript}, JavaScript, JSON, \textbf{Web API}, RESTful Services, LINQ, SQL Server 2012/2016/2019, MSTest NUnit, \textbf{Git}, Jira, \textbf{Jenkins}, \textbf{TeamCity}, \textbf{Perforce}, \textbf{Docker}, \textbf{Swarm}, \textbf{Kubernetes}, ReSharper

\section{Domain Experience}
Fulfillment System, Wealth Management, Higher Education

\section{Other Tools \& Technologies}
NodeJs, \textbf{NPM}, \textbf{GitHub}, \textbf{Visual Studio 2022/2019}, \textbf{InetelliJ IDEA}, Perforce, CFScript, CFML, Windows Server 2008/2016, \textbf{Ubuntu/Linux}, \textbf{BASH}, \textbf{rsync}, npm, \textbf{SublimeText}, \textbf{Vi}, \textbf{Gradle}, Lex/Yacc, Latex, MongoDB

\section{Professional Experience}

    %--------------------
    %     BROADRIDGE
    %--------------------

    %\vspace{0.64cm}
    \noindent
    \begin{tabular}[t]{@{}l}
    \Large{Broadridge Financial Solutions}
    \end{tabular}
    \hfill
    \begin{tabular}[t]{l@{}}
    \textbf{Deer Park NY}
    \end{tabular}
    \noindent\rule{\textwidth}{0.5pt}
    \begin{tabular}[t]{@{}l}
    Lead Software Engineer (July 2022 - Current)
    \end{tabular}
    \hfill
    \begin{tabular}[t]{l@{}}
    10 Months
    \end{tabular}
    \begin{tabular}[t]{@{}l}
    Sr. Software Engineer (April 2017 - June 2022)
    \end{tabular}
    \hfill
    \begin{tabular}[t]{l@{}}
    62 Months
    \end{tabular}

    \subsection{Company}
    Broadridge is the leading provider of investor communications \& technology-driven solutions for wealth management, asset management \& capital markets firms.

    \subsection{Responsibilities}
    Helping client with current cycle of enhancements by analyzing new requirements, preparing estimations, impact analysis documentation, \& high/low level design of proposed solutions. Responsible for \textbf{ETL} Processes for multiple Mutual Funds Clients. Creating \& Optimizing Stored Procedures/SQL queries to enhance \& optimize \textbf{Data Feed Process} for \textbf{Mutual Funds} Clients. Coordination with \textbf{off-shore team} for \textbf{end-to-end support} from \textbf{Development to Deployment}. Helping product owner in running \textbf{refinement sessions} for \textbf{scrum board}. Leading the deployment from development to production environment. Helping the agile team with completing stories in the scrum. Running \textbf{code review} sessions with other developers.


    \subsection{Environment}
    \textbf{Dotnet Core} 7.0/6.0/5.0/3.1, \textbf{C\#}, \textbf{Visual Studio 2022/2019/2017}, \textbf{SQL Server 2016}, \textbf{TeamCity}, \textbf{Jenkins}, \textbf{Git}, JavaScript, HTML, \textbf{DevOps}, \textbf{BASH}, Python, \textbf{SSIS}, \textbf{Cygwin}

    \pagebreak

    %---------------------
    %       INFOTRAX
    %---------------------

    \vspace{1.27cm}
    \noindent
    \begin{tabular}[t]{@{}l}
    \Large{InfoTrax Systems}
    \end{tabular}
    \hfill
    \begin{tabular}[t]{l@{}}
    \textbf{Auburn AL}
    \end{tabular}
    \noindent\rule{\textwidth}{0.5pt}
    \begin{tabular}[t]{@{}l}
    Software Engineer (April 2015 - March 2017)
    \end{tabular}
    \hfill
    \begin{tabular}[t]{l@{}}
    24 Months
    \end{tabular}

    \subsection{Company}
    InfoTrax enables customers to calculate distributors’ compensations with speed \& accuracy - maximizing business performance. Every feature of our software \& every service we offer is built to support the compensation plan \& the relationship between our clients \& their distributors.

    \subsection{Responsibilities}
    Involved in requirements gathering, design, development, \& customization of modules. Worked with Product Managers to apply bugs fixes \& apply customization as per client requirements. Spearheaded company-wide \textbf{Modernization Project} – applying \textbf{Industry Best Practices}. Worked on integrating \textbf{Git/Atlassian Jira} with our current WorkFlow System.

    \subsection{Environment}
    jQuery, LINQ, AngularJS, CSS, IIS, MS SQL Server 2012, ASP.NET, \textbf{.NET Framework} 4.5/4.8, \textbf{C\#} JavaScript, HTML, jQuery
    
    %\pagebreak

    %---------------------
    %       INDSTATE
    %---------------------

    \vspace{1.27cm}
    \noindent
    \begin{tabular}[t]{@{}l}
    \Large{Indiana State University}
    \end{tabular}
    \hfill
    \begin{tabular}[t]{l@{}}
    \textbf{Terre Haute IN}
    \end{tabular}
    \noindent\rule{\textwidth}{0.5pt}
    \begin{tabular}[t]{@{}l}
    Sr. Software Engineer (January 2014 - March 2015)
    \end{tabular}
    \hfill
    \begin{tabular}[t]{l@{}}
    15 Months
    \end{tabular}

    \subsection{Company}
    Institutional Research at Indiana State University produces data, analysis, \& research for the future growth, planning, \& policy making of Indiana State University, Terre Haute

    \subsection{Responsibilities}
    Full Lifecycle of the project including analysis design, development, debugging, testing, \& deployment. Developed the application from scratch using the popular MVC Framework ColdBox, ORMServices, Developed Login/Session based with auto-logout feature. Worked on UI/UX using \textbf{CSS3}, \textbf{Bootstrap}, \textbf{HTML5}. Designed \& developed \textbf{MS SQL Server 2012} Procedures, Functions, Database Triggers \& involved in creating \& updating Packages to meet business requirements. Multi-file Upload utility implemented using \textbf{jQuery}. Configured \textbf{Mura CMS} for the public site, JIRA for Issue Handling. \textbf{Grid View} with multi-filter, sort, filter, \& expandable rows with details view.

    \subsection{Environment}
    Fusebox, \textbf{ColdFusion 9/10/11}, \textbf{ColdBox}, CFScript, \textbf{MS SQL Server 2012}, JavaScript, HTML, \textbf{jQuery}, \textbf{Bootstrap}, \textbf{ExtJS (Sencha)}, Mura, IIS, Git


    %\vspace{1.27cm}
    \section{Other Projects}

    %---------------------
    %       WealthERP
    %---------------------

    %\vspace{0.64cm}
    %\noindent
    \begin{tabular}[t]{@{}l}
    \textbf{Ampsys Wealth ERP}
    \end{tabular}
    \hfill
    \begin{tabular}[t]{l@{}}
    \textbf{Bangalore, India}
    \end{tabular}
    \noindent\newline
    \begin{tabular}[t]{@{}l}
    Software Engineer (April 2013 - December 2013)
    \end{tabular}
    \hfill
    \begin{tabular}[t]{l@{}}
    9 Months
    \end{tabular}

    %---------------------
    %       CavalierIT
    %---------------------

    \vspace{0.25cm}
    \noindent
    \begin{tabular}[t]{@{}l}
    \textbf{CavalierIT}
    \end{tabular}
    \hfill
    \begin{tabular}[t]{l@{}}
    \textbf{Edison, NJ}
    \end{tabular}
    \noindent\newline
    \begin{tabular}[t]{@{}l}
    Software Engineer (October 2011 - March 2013)
    \end{tabular}
    \hfill
    \begin{tabular}[t]{l@{}}
    18 Months
    \end{tabular}

    %---------------------
    %       Indstate
    %---------------------

    \vspace{0.25cm}
    \noindent
    \begin{tabular}[t]{@{}l}
    \textbf{Indiana State University}
    \end{tabular}
    \hfill
    \begin{tabular}[t]{l@{}}
    \textbf{Terre Haute, IN}
    \end{tabular}
    \noindent\newline
    \begin{tabular}[t]{@{}l}
    Software Engineer (January 2010 - August 2011)
    \end{tabular}
    \hfill
    \begin{tabular}[t]{l@{}}
    20 Months
    \end{tabular}

    %---------------------
    %       IITK
    %---------------------

    \vspace{0.25cm}
    \noindent
    \begin{tabular}[t]{@{}l}
    \textbf{Indian Institute of Technology Kanpur}
    \end{tabular}
    \hfill
    \begin{tabular}[t]{l@{}}
    \textbf{Kanpur, India}
    \end{tabular}
    \noindent\newline
    \begin{tabular}[t]{@{}l}
    Software Engineer (July 2007 - June 2009)
    \end{tabular}
    \hfill
    \begin{tabular}[t]{l@{}}
    24 Months
    \end{tabular}
    
    \section{Education}
    \begin{itemize}
    	\item \textbf{Masters in Computer Science}, Indiana State University
    	\item \textbf{Bachelors in Computer Science \& Engineering}, Dr. A.P.J. Abdul Kalam Technical University
    \end{itemize}
    
    
    \end{document}